Torrential Twitter? Measuring the Severity of Harassment when Canadian Female Politicians Tweet about Climate Change

### 2024-02-15 Outputs/Paper/Publication_version/paper_for_pub.qmd
minor updates

ggplot(harassment_model_predictions, aes(harassment_binary, estimate)) +
  geom_jitter(aes(colour = factor(name_of_politician))) +
  facet_wrap(verified ~type_of_account) +
  labs(
    x = "Whether a Tweet contains harassment",
    y = "Estimated probability that a \nTweet contains harassment",
    color = "Name of Politician"
  ) +
  theme(legend.position = "bottom") +
  theme(axis.text.x = element_text(angle=45, hjust = 1, size = 7)) +
  theme(axis.text.y = element_text(size = 6)) + 
  scale_colour_manual(values = c("darkblue", "darkcyan", "yellow"))

@@

combined_apple_data |>
  select(name) |>
  slice_tail(n = 5) |>
  kable(
    col.names = c("Name"),
    booktabs = TRUE,
  )
```

>>>>

ggplot(harassment_model_predictions, aes(harassment_binary, estimate)) +
  geom_jitter(aes(colour = factor(name_of_politician))) +
  facet_wrap(verified ~type_of_account) +
  labs(
    x = "Whether a Tweet contains harassment",
    y = "Estimated probability that a \nTweet contains harassment",
    color = "Name of Politician"
  ) +
  theme_bw() +
  theme(legend.position = "bottom") +
  theme(axis.text.x = element_text(angle=45, hjust = 1, size = 7)) +
  theme(axis.text.y = element_text(size = 6)) + 
  scale_colour_manual(values = c("darkblue", "darkcyan", "yellow"))

@@

combined_apple_data |>
  select(name) |>
  slice_tail(n = 5) |>
  kable(
    col.names = c("Name"),
    booktabs = TRUE,
    linesep = ""
  )
```
